---
title: "Using plot_histogram"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{plot_histogram-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}{inputenc}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(EDAhelperR)
data <- iris
```

## Create histograms for all numeric columns

The function `plot_histogram` will generate histograms for all numeric columns in a given data frame by default.
```{r}
plot_histogram(data)
```

## Create histogram for specific columns
Specific columns in the data frame can be plotted by assigning a character vector of column names to the `columns` argument.
```{r}
plot_histogram(data, columns = c("Sepal.Length", "Sepal.Width"))
```


## Adjust number of bins on plot
The number of bins on the plot can be adjusted by providing a numeric value to the `num_bins` argument.
```{r}
plot_histogram(data, columns = c("Sepal.Length", "Sepal.Width"), num_bins = 20)
```
